\documentclass{article}

% Packages
\usepackage[utf8]{inputenc} % UTF-8 encoding
\usepackage{geometry}       % For proper margins
\geometry{a4paper, margin=1in}

% Document starts here
\begin{document}

% Title
\title{Table of Contents}
\author{}
\date{}
\maketitle

% Table of Contents with Roman numbering
\pagenumbering{roman}
\setcounter{page}{1} % Start Roman numbering at i
\tableofcontents
\clearpage

% Switch to Arabic numbering for sections
\pagenumbering{arabic}

% Introduction
\section*{Bisection Method for Root Finding}
\addcontentsline{toc}{section}{Bisection Method for Root Finding}
\setcounter{page}{1} % Start at page 5
Content for Introduction goes here.
\clearpage

% False Position Method for Root Finding
\section*{False Position Method for Root Finding}
\addcontentsline{toc}{section}{False Position Method for Root Finding}
\setcounter{page}{2} % Start at page 10
Content for False Position Method for Root Finding goes here.
\clearpage

% Secant Method for Root Finding
\section*{Secant Method for Root Finding}
\addcontentsline{toc}{section}{Secant Method for Root Finding}
\setcounter{page}{3} % Start at page 15
Content for Secant Method for Root Finding goes here.
\clearpage

% Gauss-Seidel Method for Solving Linear Systems
\section*{Gauss-Seidel Method for Solving Linear Systems}
\addcontentsline{toc}{section}{Gauss-Seidel Method for Solving Linear Systems}
\setcounter{page}{4} % Start at page 20
Content for Gauss-Seidel Method for Solving Linear Systems goes here.
\clearpage

% Least Squares Regression Method for Data Fitting
\section*{Least Squares Regression Method for Data Fitting}
\addcontentsline{toc}{section}{Least Squares Regression Method for Data Fitting}
\setcounter{page}{5} % Start at page 25
Content for Least Squares Regression Method for Data Fitting goes here.
\clearpage

% Fitting Transcendental Equations for Curve Derivation
\section*{Fitting Transcendental Equations for Curve Derivation}
\addcontentsline{toc}{section}{Fitting Transcendental Equations for Curve Derivation}
\setcounter{page}{6} % Start at page 30
Content for Fitting Transcendental Equations for Curve Derivation goes here.
\clearpage

% Fitting Transcendental Equations for Curve Derivation
\section*{Euler Method for Solving Ordinary Differential Equations}
\addcontentsline{toc}{section}{Euler Method for Solving Ordinary Differential Equations}
\setcounter{page}{7} % Start at page 30
Content for Euler Method for Solving Ordinary Differential Equations goes here.
\clearpage

% Fitting Transcendental Equations for Curve Derivation
\section*{Cramer`s Rule for Solving Linear Systems}
\addcontentsline{toc}{section}{Cramer`s Rule for Solving Linear Systems}
\setcounter{page}{8} % Start at page 30
Content for Cramer`s Rule for Solving Linear Systems goes here.
\clearpage

% Fitting Transcendental Equations for Curve Derivation
\section*{Simpson's 1/3 Rule for Numerical Integration}
\addcontentsline{toc}{section}{Simpson's 1/3 Rule for Numerical Integration}
\setcounter{page}{10} % Start at page 30
Content for Simpson's 1/3 Rule for Numerical Integration goes here.
\clearpage

% Fitting Transcendental Equations for Curve Derivation
\section*{Simpson's 3/8 Rule for Numerical Integration}
\addcontentsline{toc}{section}{Simpson's 3/8 Rule for Numerical Integration}
\setcounter{page}{11} % Start at page 30
Content for Simpson's 3/8 Rule for Numerical Integration goes here.
\clearpage
% Fitting Transcendental Equations for Curve Derivation
\section*{Trapezoidal Rule for Numerical Integration}
\addcontentsline{toc}{section}{Trapezoidal Rule for Numerical Integration}
\setcounter{page}{12} % Start at page 30
Content for Trapezoidal Rule for Numerical Integration goes here.
\clearpage

\end{document}
